### 2025-09-23 paper/sec/authoring-workflow.tex
Prep for IA summary.

Figure~\ref{fig:overall-architecture} shows the system architecture and an example flow.
The system is composed of two agents:

\begin{itemize}
    \item \textbf{\SuggestionAgent}. LLM-based agent which identifies text fragments potentially computable from data.
    \item \textbf{\InterpretationAgent}. LLM-based agent which, for a given text fragment (provided by
    SuggestionAgent or by the author), attempts to synthesise a Fluid expression computing the target text.
\end{itemize}

@@

Figure~\ref{fig:interpretation-agent} shows the overall architecture of the \InterpretationAgent. The author
initially provides the text and accompanying data. The \SuggestionAgent analyses the input and identifies
candidate fragments of natural language which could be replaced by Fluid expressions. The user highlightes a
fragment of interest, which is then sent to the \InterpretationAgent, which generates a corresponding
candidate expression. Internally the \InterpretationAgent uses a compiler-in-the-loop validation process to
ensure the expression is well-formed. The user is then able to accept the expression (in which case it is
incorporated into the program) or reject and leave the text uninterpreted.

>>>>

Figure~\ref{fig:overall-architecture} shows the system architecture and an example flow.
The system is composed of two LLM-based agents:

\begin{itemize}
    \item \textbf{\SuggestionAgent}. Identifies text fragments potentially computable from data.
    \item \textbf{\InterpretationAgent}. For a given text fragment (provided by SuggestionAgent or author),
    attempts to synthesise Fluid expression computing target fragment.
\end{itemize}

@@

The author initially provides the text and accompanying data. The \SuggestionAgent analyses the inputs and
identifies candidate fragments of natural language which could be replaced by Fluid expressions.
Figure~\ref{fig:interpretation-agent} then shows the overall workflow of the \InterpretationAgent, with the
human author in the loop. The user highlights a fragment of interest, which is then sent to the
\InterpretationAgent, which generates a corresponding candidate expression. Internally the
\InterpretationAgent uses a compiler-in-the-loop validation process to ensure the expression is well-formed.
The user is then able to accept the expression (in which case it is incorporated into the program) or reject
and leave the text uninterpreted.
